Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2014-12-17 content/appendix.tex
pass through appendix/proofs

%OL: Again, we can keep it simpler:
For the other direction:
\begin{align*}
&&
    \denote{\setpair{I}{U}} &= \denote{\setpair{I'}{U'}}\\
&\implies &
    \denote{\setpair{I}{U}}(\lambda r. \emptyset) &= \denote{\setpair{I'}{U'}}(\lambda r. \emptyset)\\
&\implies &
(\lambda m.\lambda r.(m(r)\cap I(r))\cup U(r))(\lambda r.\emptyset) &=
(\lambda m.\lambda r.(m(r)\cap I'(r))\cup U'(r))(\lambda r.\emptyset) \\
&\implies &
\lambda r.(\emptyset \cap I(r))\cup U(r) &=
\lambda r.(\emptyset \cap I'(r))\cup U'(r) \\
&\implies &
\lambda r.U(r) &=
\lambda r.U'(r) \\
&\implies &
U &=
U' \\
\end{align*}
Similarly:
\begin{align*}
&&
    \denote{\setpair{I}{U}} &= \denote{\setpair{I'}{U'}}\\
&\implies &
\denote{\setpair{I}{U}}(I) &= \denote{\setpair{I'}{U'}}(I)\\
&\implies &
(\lambda m.\lambda r.(m(r)\cap I(r))\cup U(r))(I) &=
(\lambda m.\lambda r.(m(r)\cap I'(r))\cup U'(r))(I) \\
&\implies &
\lambda r.(I(r) \cap I(r))\cup U(r) &=
\lambda r.(I(r) \cap I'(r))\cup U'(r) \\
&\implies &
\lambda r.(I(r) \cap I(r)) &=
\lambda r.(I(r) \cap I'(r)) \textrm{ since $\forall r.U(r) \subseteq I(r)$} \\
&\implies \forall r.&
I(r) &= I(r) \cap I'(r)\\
&\implies \forall r.&
I(r) &\subseteq I'(r)\\
\end{align*}
\mtodo{I agree that this is much better than what I had. I think from $I(r) = I(r) \cap I'(r)$ we can conclude that $I(r)=I'(r)$.}
Symmetrically, we can also establish that $\forall r.I'(r) \subseteq I(r)$ by applying the functions to $I'$ instead of to $I$. Therefore, $I = I'$.
\end{proof}

\equalComp*
\otodo{The (m)(r) does not seem necessary. Can we replace $r'$ with $r$ and $m'$ with $m$?}
\begin{proof}
\begin{align*}
  &\denote{\setpair IU\circ\setpair{I'}{U'}}\\
  =&\denote{\setpair{\lambda r\,.\,(I(r')\cap I'(r))\cup U(r)}
                    {\lambda r\,.\,(I(r)\cap U'(r))\cup U(r)}}\\
  =&\lambda m\,.\,\lambda r\,.\,(m(r)\cap(I(r)\cap I'(r))\cup U(r))\cup(I(r)\cap U'(r))\cup U(r)\\
  =&\lambda m\,.\,\lambda r\,.\,(m(r)\cap I'(r))\cup I(r)\cup (U'(r)\cap I(r))\cup U(r)\\
  =&\lambda m\,.\,\lambda r\,.\,(((m(r)\cap I'(r))\cup U'(r))\cap I(r))\cup U(r)\\
  =&\lambda m\,.\,\lambda r\,.\,(((m(r)\cap I'(r))\cup U'(r))\cap I(r))\cup U(r)\\
  =&\lambda m\,.\,\left(\lambda m'\,.\,\lambda r\,.\,(m'(r)\cap I(r))\cup U(r)\right)
    \left(
    \left(\lambda r\,.\,(m(r)\cap I'(r))\cup U'(r)\right)
    \right)\\
  =&\left(\lambda m\,.\,\lambda r\,.\,(m(r)\cap I(r))\cup U(r)\right)\circ
    \left(\lambda m\,.\,\lambda r\,.\,(m(r)\cap I'(r))\cup U'(r)\right)\\
  =&\denote{\setpair IU}\circ\denote{\setpair{I'}{U'}}.\qedhere
\end{align*}
\end{proof}

@@

For the purpose of the proofs, we will rewrite Equation~\eqref{eq:edgefndef} that defines an edge function as follows:
  \begin{equation}\label{eq:edgefnThroughDelta}
    \ccedgefn S=\lambda e\,.\,
    \begin{cases}
      \id&\text{if $d_1=d_2=\Lambda$,}\\
      \lambda m\,.\,\varepsilon(e)(\delta(m))&\text{otherwise},
    \end{cases}
  \end{equation}
  where $S\subseteq R$, $d_1$ and $d_2$ are the source and target facts, and for a map $m\in\lcc_U$, $\delta(m)$ is either $m$ or $\botcc$:
  \begin{equation}\label{eq:deltadef}
    \delta(m)=\begin{cases}
      \botcc&\text{if $d_1=\Lambda$}\\
      m&\text{otherwise.}
    \end{cases}
  \end{equation}

@@

  For each $i$, let $e_i$ be the edge $((n_{i-1},\,d_{i-1}),\,(n_i,\,d_i))$. Note that $$e_1=((\startmain,\,\Lambda),\,(n_1,\,d_1))\,.$$

@@

As shown in~Sagiv et al.~\cite{sagiv1996precise}, the relationship between environment transformers and edge functions can be described with the following equation. For an edge $(n_1,\,n_2)\in E^*$ an environment $\textsf{env}$ that maps $D$ to $L$, and a fact $d\in D$,
\begin{align}\label{eq:envTransToEdgeFnEdge}
  \menv&((n_1,\,n_2))(\textsf{env})(d)\notag\\
  &=\edgefn((n_1,\,\Lambda),\,(n_2,\,d))(\top)\sqcap\bigsqcap_{d'\in D}\edgefn((n_1,\,d'),\,(n_2,\,d))(\textsf{env}(d'))\,.
\end{align}  
Then, according to~\eqref{eq:envTransToEdgeFnEdge},\mtodo{Is it okay that in~\eqref{eq:envTransToEdgeFnEdge}, we use $\edgefn$, and below we use $\ccedgefn R$?}
  \begin{align*}
    &\menv(e_k)\left(\menv(p)(\top_\textsf{Env})\right)(d)(r)\\
      =&\bigg(\ccedgefn R((n_{k-1},\,\Lambda),\,(n_k,\,d))(\topcc)\sqcap\\
       &\bigsqcap_{d'\in D}\ccedgefn R((n_{k-1},\,d'),\,(n_k,\,d))(\menv(p)(\top_\textsf{Env})(d'))\bigg)(r)\\
      \supseteq&
        \bigsqcap_{d'\in D}\ccedgefn R((n_{k-1},\,d'),\,(n_k,\,d))(\menv(p)(\top_\textsf{Env})(d'))(r)\\
      \supseteq&\,\ccedgefn R((n_{k-1},\,d_{k-1}),\,(n_k,\,d))(\mpdkm)(r)\,.
  \end{align*}
  Therefore, 
  \begin{equation}\label{eq:musubset}
    \efek\subseteq\mppd(r)\,.
  \end{equation}

@@

  If $d_{k-1}=d_k=\Lambda$, then $d_k\notin M_F(p)(\varnothing)$, since it does not belong to the set $D$, and the Lemma trivially holds.

@@

  \textit{Basis:} 
    Let $p=[\startmain]$. Since the only realizable path corresponding to $p$ is $[(\startmain,\,\Lambda)]$, there is no fact $d\in D$ such that $d\in M_F(p)(\varnothing)$, and the claim follows immediately.

@@

\precision*
\begin{proof}
    \otodo{It's Section 3.2.}
    \mtodo{Section 3.2 talks about the IFDS algorithm, but it doesn't explicitly say how the result of an IFDS analysis looks like and doesn't introduce the notation $\resultIFDS$.}
  Let $P$ be an IFDS problem. Recall from Section~\ref{sec:ideToIfds} that the result of an IFDS analysis $\resultIFDS(P)$ maps supergraph
  nodes $n\in N^*$ to sets of data-flow facts $\delta\in2^D$. Specifically,
  \begin{align*}
    \resultIFDS(P)&=\lambda n\,.\,\mvp F(n)\\
    &=\bigsqcap_{q\in\textsf{VP}(n)}M_F(q)(\top).
  \end{align*}
  At the same time,
  \begin{align*}
    \backCC\left(\resultIDE(\transCC_R(P))\right)(n)
    &=\left\{d\,|\,\forall r\in R\,.\,\resultIDE(\transCC_R(P))(n)(d)(r)\ne\top_T\right\}\\
    &=\left\{d\,|\,\forall r\in R\,.\,\bigsqcap_{q\in\textsf{VP}(n)}\xi(q,\,d)(r)\ne\top_T\right\}.
  \end{align*}
  This means that for any given $d\in\backCC(\resultIDE(\transCC R(P)))(n)$ and path $q\in\textsf{VP}(n)$, $\xi(q,\,d)\ne\top_T$. Therefore, according to~Lemma~\ref{lem:sound3}, $d\in M_F(q)(\top)$. It follows that $d\in\bigsqcap_{q\in\textsf{VP}(n)}M_F(q)(\top)$, which is equal to $\resultIFDS(P)(n)$. 
  Hence, we have shown that if $d\in\backCC(\resultIDE(\transCC R(P)))(n)$, then $d\in\resultIFDS(P)(n)$.
\end{proof}

@@

\begin{lemma}\label{lem:recindepedgefn}
  Let $P$ be an IFDS problem. Let $N^*$ be the supergraph for $P$, $D$ the set of data-flow facts, $n\in N^*$ a node, and $p=[\startmain,\,\dots,\,n]$ a path in the supergraph. Let $d\in D\cup\{\Lambda\}$.
  Then for any realizable path $p'\in\textsf{RP}(p,\,d)$, set $S\subseteq R$, and receiver $r\in S$,
  \begin{equation}
    \ccedgefn S(p')(\topcc)(r)=
    \ccedgefn{\{r\}}(p')(\topcc)(r)\,.
  \end{equation}
\end{lemma}
\begin{proof}
  By induction on the length of $p$.

  \textit{Basis:} $p'=[(\startmain,\,\Lambda)]$. Then $\ccedgefn S(p')=\id=\ccedgefn{\{r\}}(p')$, and the Lemma follows directly.

  \textit{Induction hypothesis:} Suppose that for a path $q=[(\startmain,\,\Lambda),\,\dots,\,(n_{k-1},\,d_{k-1})]$, where $q\in\textsf{RP}(n,\,d)$, the Lemma holds, i.e. both edge functions map $r$ to the same set of types $\uptau$:
  \begin{align*}
    \uptau
    &=\ccedgefn S(q)(\topcc)(r)\\
    &=\ccedgefn{\{r\}}(q)(\topcc)(r)\,.
  \end{align*}

  \textit{Induction step:} Let $q'=[(\startmain,\,\Lambda),\,\dots,\,(n_{k-1},\,d_{k-1}),\,(n_k,\,d_k)]$ and the edge $e_k=((n_{k-1},\,d_{k-1}),\,(n_k,\,d_k))$.

@@

  If $d_{k-1}=d_k=\Lambda$, $\ccedgefn S(e_k)=\id=\ccedgefn{\{r\}}(e_k)$, and, due to~\eqref{eq:edgefnU},
  \begin{align*}
    \ccedgefn S(q')(\topcc)(r)&=\uptau\\
    &=\ccedgefn{\{r\}}(q')(\topcc)(r)\,.
  \end{align*}

  Otherwise, there are four sub-cases.
  \begin{enumerate}
    \item $e_k$ is a call-start edge, $r'.c()$ is the call site at $n_{k-1}$ with signature $s$, $f$ is the called procedure, and $r'\in U$.
    Then
    \[
      \ccedgefn U(e_k)=\lambda m\,.\,\delta(m)[r'\to\delta(m)(r)\cap\tau(s,\,f)]\,.
    \]
    There are two sub-cases.
    \begin{enumerate}
      \item\label{item:callstartreceq} If $r=r'$, then, according to~\eqref{eq:edgefnU}, the resulting set of types 
        \[
          \ccedgefn U(q')(\topcc)(r)=\delta(\ccedgefn U(q)(\topcc))(r)\cap\tau(s,\,f).
        \]
        If $d_{k-1}=\Lambda$, then $\delta(\ccedgefn U(q)(\topcc))(r)=\botcc(r)=\bot_T$. If $d_{k-1}\ne\Lambda$, then $\delta(\ccedgefn U(q)(\topcc))(r)=\ccedgefn U(q)(\topcc)(r)=\uptau$. The set $\tau(s,\,f)$ is the same for either case.

@@

The next lemma shows that the set of types to which a receiver is mapped in a correlated-calls lattice element can be represented as an intersection of static-type function applications $\tau(s_i,\,f_i)$.
\begin{lemma}\label{lem:edgefnThroughTaus}
  For an IFDS problem $P$, a node $n\in N^*$, and fact $d\in D$, let $p\in\mathsf{RP}(n,\,d)$ be a realizable path and $r\in R$ a receiver. Then there exists a non-negative number $\gamma$ of calls on the receiver $r$ with signatures $s_\gamma$ to the functions~$f_\gamma$, for which
  \[
    \ccedgefn{\{r\}}(p)(\topcc)(r)=
      \bigcap_{\gamma\ge0}\tau(s_\gamma,\,f_\gamma)\,.
  \]
\end{lemma}
\begin{proof}
  Let $p$ have the following form\footnote{It can be shown from the definition of a pointwise representation in~Sagiv et al.~\cite{sagiv1996precise} that in a realizable path, there is never an edge from a fact of the set $D$ to a $\Lambda$ fact. Therefore, we can represent $p$ as a sequence of nodes that has a prefix of $\Lambda$-fact nodes, after which all nodes are non-$\Lambda$ facts.}:
  \[
    p=[(\startmain,\,\Lambda),\,(n_1,\,\Lambda),\,\dots,\,(n_k,\,\Lambda),
       (n_{k+1},\,d_{k+1}),\,\dots,\,(n_{k+l},\,d_{k+l})]\,,
  \]
  where $l\ge1$ and the facts for all nodes up to $n_k$ are equal to $\Lambda$ and $d_{k+i}\in D$ for $0<i\le l$.

@@

  From~\eqref{eq:edgefndef} we can infer that
  \[
    \ccedgefn{\{r\}}(p)=
    \ccedgefn{\{r\}}(e_{k+l})
    \circ\ldots
    \circ\ccedgefn{\{r\}}(e_{k+2})
    \circ(\lambda m\,.\,\beta)
    \circ\id
    \circ\ldots
    \circ\id\,,
  \]
  where
  \[
    \beta=
    \begin{cases}
      \botcc[r\to\tau(s,\,f)]&\text{if $(n_k,\,n_{k+1})$ is a call-start or end-return edge, and}\\&\text{the call site $r.c()$ with signature $s$ to the function}\\
      &\text{$f$ corresponds to the call-start or end-return edge,}\\
      \botcc&\text{otherwise\footnotemark.}
    \end{cases}
  \]
  \footnotetext{Since $d_k=\Lambda$ and $d_{k+1}\ne\Lambda$, the micro function for the edge $e_{k+1} $ is equal to $\lambda m\,.\,\varepsilon_{\{r\}}(e_{k+1})(\botcc)$. From the definition of $\varepsilon_S$~\eqref{eq:varepsilon} we can see that the only case where $\varepsilon_{\{r\}}(e_{k+1})(m)$ would not be equal to $\botcc$ is when $e_{k+1}$ is call-start or end-return edge.}

@@

\textit{Induction hypothesis:}
Assume that for a path $p=[(\startmain,\,\Lambda),\,\dots,\,(n_{k+l},\,d_{k+l})]$, the Lemma holds for $\gamma=N$, where $N\ge0$.

\textit{Induction step:}
Let $p'=[(\startmain,\,\Lambda),\,\dots,\,(n_{k+l},\,d_{k+l}),\,(n_{k+l+1},\,d_{k+l+1})]$.

@@

>>>>

%OL: Again, we can keep it simpler:
For the other direction:
\begin{align*}
&&
    \denote{\setpair{I}{U}} &= \denote{\setpair{I'}{U'}}\\
&\implies &
    \denote{\setpair{I}{U}}(\lambda r. \emptyset) &= \denote{\setpair{I'}{U'}}(\lambda r. \emptyset)\\
&\implies &
(\lambda m.\lambda r.(m(r)\cap I(r))\cup U(r))(\lambda r.\emptyset) &=
(\lambda m.\lambda r.(m(r)\cap I'(r))\cup U'(r))(\lambda r.\emptyset) \\
&\implies &
\lambda r.(\emptyset \cap I(r))\cup U(r) &=
\lambda r.(\emptyset \cap I'(r))\cup U'(r) \\
&\implies &
\lambda r.U(r) &=
\lambda r.U'(r) \\
&\implies &
U &=
U' \\
\end{align*}
Similarly:
\begin{align*}
&&
    \denote{\setpair{I}{U}} &= \denote{\setpair{I'}{U'}}\\
&\implies &
\denote{\setpair{I}{U}}(I) &= \denote{\setpair{I'}{U'}}(I)\\
&\implies &
(\lambda m.\lambda r.(m(r)\cap I(r))\cup U(r))(I) &=
(\lambda m.\lambda r.(m(r)\cap I'(r))\cup U'(r))(I) \\
&\implies &
\lambda r.(I(r) \cap I(r))\cup U(r) &=
\lambda r.(I(r) \cap I'(r))\cup U'(r) \\
&\implies &
\lambda r.(I(r) \cap I(r)) &=
\lambda r.(I(r) \cap I'(r)) \textrm{ since $\forall r.U(r) \subseteq I(r)$} \\
&\implies \forall r.&
I(r) &= I(r) \cap I'(r)\\
&\implies \forall r.&
I(r) &\subseteq I'(r)\\
\end{align*}
%\mtodo{I agree that this is much better than what I had. I think from $I(r) = I(r) \cap I'(r)$ we can conclude that $I(r)=I'(r)$.}
%\otodo{No. {1,2} = {1,2} \cap {1,2,3}, but {1,2} is not equal to {1,2,3}.}
Symmetrically, we can also establish that $\forall r.I'(r) \subseteq I(r)$ by applying the functions to $I'$ instead of to $I$. Therefore, $I = I'$.
\end{proof}

\equalComp*
%\otodo{The (m)(r) does not seem necessary. Can we replace $r'$ with $r$ and $m'$ with $m$?}
\begin{proof}
\begin{align*}
  &\denote{\setpair IU\circ\setpair{I'}{U'}}\\
  =&\denote{\setpair{\lambda r\,.\,(I(r')\cap I'(r))\cup U(r)}
                    {\lambda r\,.\,(I(r)\cap U'(r))\cup U(r)}}\\
  =&\lambda m\,.\,\lambda r\,.\,(m(r)\cap(I(r)\cap I'(r))\cup U(r))\cup(I(r)\cap U'(r))\cup U(r)\\
  =&\lambda m\,.\,\lambda r\,.\,(m(r)\cap I'(r))\cup I(r)\cup (U'(r)\cap I(r))\cup U(r)\\
  =&\lambda m\,.\,\lambda r\,.\,(((m(r)\cap I'(r))\cup U'(r))\cap I(r))\cup U(r)\\
  =&\lambda m\,.\,\left(\lambda m'\,.\,\lambda r\,.\,(m'(r)\cap I(r))\cup U(r)\right)
    \left(
    \left(\lambda r\,.\,(m(r)\cap I'(r))\cup U'(r)\right)
    \right)\\
  =&\left(\lambda m\,.\,\lambda r\,.\,(m(r)\cap I(r))\cup U(r)\right)\circ
    \left(\lambda m\,.\,\lambda r\,.\,(m(r)\cap I'(r))\cup U'(r)\right)\\
  =&\denote{\setpair IU}\circ\denote{\setpair{I'}{U'}}.\qedhere
\end{align*}
\end{proof}

@@

For the purpose of the proofs, we will rewrite Equation~\eqref{eq:edgefndef} that defines an edge function as follows:
  \begin{equation}\label{eq:edgefnThroughDelta}
    \ccedgefn S=\lambda e\,.\,
    \begin{cases}
      \id&\text{if $d_1=d_2=\mathbf0$,}\\
      \lambda m\,.\,\varepsilon(e)(\delta(m))&\text{otherwise},
    \end{cases}
  \end{equation}
  where $S\subseteq R$, $d_1$ and $d_2$ are the source and target facts, and for a map $m\in\lcc_U$, $\delta(m)$ is either $m$ or $\botcc$:
  \begin{equation}\label{eq:deltadef}
    \delta(m)=\begin{cases}
      \botcc&\text{if $d_1=\mathbf0$}\\
      m&\text{otherwise.}
    \end{cases}
  \end{equation}

@@

  For each $i$, let $e_i$ be the edge $((n_{i-1},\,d_{i-1}),\,(n_i,\,d_i))$. Note that $$e_1=((\startmain,\,\mathbf0),\,(n_1,\,d_1))\,.$$

@@

As shown in~Sagiv et al.~\cite{sagiv1996precise}, the relationship between environment transformers and edge functions can be described with the following equation. For an edge $(n_1,\,n_2)\in E^*$ an environment $\textsf{env}$ that maps $D$ to $L$, and a fact $d\in D$,
\begin{align}\label{eq:envTransToEdgeFnEdge}
  \menv&((n_1,\,n_2))(\textsf{env})(d)\notag\\
  &=\edgefn((n_1,\,\mathbf0),\,(n_2,\,d))(\top)\sqcap\bigsqcap_{d'\in D}\edgefn((n_1,\,d'),\,(n_2,\,d))(\textsf{env}(d'))\,.
\end{align}  
Then, according to~\eqref{eq:envTransToEdgeFnEdge},
%\mtodo{Is it okay that in~\eqref{eq:envTransToEdgeFnEdge}, we use $\edgefn$, and below we use $\ccedgefn R$?}
%\otodo{Yes, that's fine.}
  \begin{align*}
    &\menv(e_k)\left(\menv(p)(\top_\textsf{Env})\right)(d)(r)\\
      =&\bigg(\ccedgefn R((n_{k-1},\,\mathbf0),\,(n_k,\,d))(\topcc)\sqcap\\
       &\bigsqcap_{d'\in D}\ccedgefn R((n_{k-1},\,d'),\,(n_k,\,d))(\menv(p)(\top_\textsf{Env})(d'))\bigg)(r)\\
      \supseteq&
        \bigsqcap_{d'\in D}\ccedgefn R((n_{k-1},\,d'),\,(n_k,\,d))(\menv(p)(\top_\textsf{Env})(d'))(r)\\
      \supseteq&\,\ccedgefn R((n_{k-1},\,d_{k-1}),\,(n_k,\,d))(\mpdkm)(r)\,.
  \end{align*}
  Therefore, 
  \begin{equation}\label{eq:musubset}
    \efek\subseteq\mppd(r)\,.
  \end{equation}

@@

  If $d_{k-1}=d_k=\mathbf0$, then $d_k\notin M_F(p)(\varnothing)$, since it does not belong to the set $D$, and the Lemma trivially holds.

@@

  \textit{Basis:} 
    Let $p=[\startmain]$. Since the only realizable path corresponding to $p$ is $[(\startmain,\,\mathbf0)]$, there is no fact $d\in D$ such that $d\in M_F(p)(\varnothing)$, and the claim follows immediately.

@@

\precision*
\begin{proof}
    %\otodo{It's Section 3.2.}
    %\mtodo{Section 3.2 talks about the IFDS algorithm, but it doesn't explicitly say how the result of an IFDS analysis looks like and doesn't introduce the notation $\resultIFDS$.}
  Let $P$ be an IFDS problem. Recall from Section~\ref{sec:ideToIfds} that the result of an IFDS analysis $\resultIFDS(P)$ maps supergraph
  nodes $n\in N^*$ to sets of data-flow facts $\delta\in2^D$. Specifically,
  \begin{align*}
    \resultIFDS(P)&=\lambda n\,.\,\mvp F(n)\\
    &=\bigsqcap_{q\in\textsf{VP}(n)}M_F(q)(\top).
  \end{align*}
  At the same time,
  \begin{align*}
    \backCC\left(\resultIDE(\transCC_R(P))\right)(n)
    &=\left\{d\,|\,\forall r\in R\,.\,\resultIDE(\transCC_R(P))(n)(d)(r)\ne\top_T\right\}\\
    &=\left\{d\,|\,\forall r\in R\,.\,\bigsqcap_{q\in\textsf{VP}(n)}\xi(q,\,d)(r)\ne\top_T\right\}.
  \end{align*}
  This means that for any given $d\in\backCC(\resultIDE(\transCC R(P)))(n)$ and path $q\in\textsf{VP}(n)$, $\xi(q,\,d)\ne\top_T$. Therefore, according to~Lemma~\ref{lem:sound3}, $d\in M_F(q)(\top)$. It follows that $d\in\bigsqcap_{q\in\textsf{VP}(n)}M_F(q)(\top)$, which is equal to $\resultIFDS(P)(n)$. 
  Hence, we have shown that if $d\in\backCC(\resultIDE(\transCC R(P)))(n)$, then $d\in\resultIFDS(P)(n)$.
\end{proof}

@@

\begin{lemma}\label{lem:recindepedgefn}
  Let $P$ be an IFDS problem. Let $N^*$ be the supergraph for $P$, $D$ the set of data-flow facts, $n\in N^*$ a node, and $p=[\startmain,\,\dots,\,n]$ a path in the supergraph. Let $d\in D\cup\{\mathbf0\}$.
  Then for any realizable path $p'\in\textsf{RP}(p,\,d)$, set $S\subseteq R$, and receiver $r\in S$,
  \begin{equation}
    \ccedgefn S(p')(\topcc)(r)=
    \ccedgefn{\{r\}}(p')(\topcc)(r)\,.
  \end{equation}
\end{lemma}
\begin{proof}
  By induction on the length of $p$.

  \textit{Basis:} $p'=[(\startmain,\,\mathbf0)]$. Then $\ccedgefn S(p')=\id=\ccedgefn{\{r\}}(p')$, and the Lemma follows directly.

  \textit{Induction hypothesis:} Suppose that for a path $q=[(\startmain,\,\mathbf0),\,\dots,\,(n_{k-1},\,d_{k-1})]$, where $q\in\textsf{RP}(n,\,d)$, the Lemma holds, i.e. both edge functions map $r$ to the same set of types $\uptau$:
  \begin{align*}
    \uptau
    &=\ccedgefn S(q)(\topcc)(r)\\
    &=\ccedgefn{\{r\}}(q)(\topcc)(r)\,.
  \end{align*}

  \textit{Induction step:} Let $q'=[(\startmain,\,\mathbf0),\,\dots,\,(n_{k-1},\,d_{k-1}),\,(n_k,\,d_k)]$ and the edge $e_k=((n_{k-1},\,d_{k-1}),\,(n_k,\,d_k))$.

@@

  If $d_{k-1}=d_k=\mathbf0$, $\ccedgefn S(e_k)=\id=\ccedgefn{\{r\}}(e_k)$, and, due to~\eqref{eq:edgefnU},
  \begin{align*}
    \ccedgefn S(q')(\topcc)(r)&=\uptau\\
    &=\ccedgefn{\{r\}}(q')(\topcc)(r)\,.
  \end{align*}

  Otherwise, there are four sub-cases.
  \begin{enumerate}
    \item $e_k$ is a call-start edge, $r'.c()$ is the call site at $n_{k-1}$ with signature $s$, $f$ is the called procedure, and $r'\in U$.
    Then
    \[
      \ccedgefn U(e_k)=\lambda m\,.\,\delta(m)[r'\to\delta(m)(r)\cap\tau(s,\,f)]\,.
    \]
    There are two sub-cases.
    \begin{enumerate}
      \item\label{item:callstartreceq} If $r=r'$, then, according to~\eqref{eq:edgefnU}, the resulting set of types 
        \[
          \ccedgefn U(q')(\topcc)(r)=\delta(\ccedgefn U(q)(\topcc))(r)\cap\tau(s,\,f).
        \]
        If $d_{k-1}=\mathbf0$, then $\delta(\ccedgefn U(q)(\topcc))(r)=\botcc(r)=\bot_T$. If $d_{k-1}\ne\mathbf0$, then $\delta(\ccedgefn U(q)(\topcc))(r)=\ccedgefn U(q)(\topcc)(r)=\uptau$. The set $\tau(s,\,f)$ is the same for either case.

@@

The next lemma shows that the set of types to which a receiver is mapped in a correlated-calls lattice element can be represented as an intersection of static-type function applications $\tau(s_i,\,f_i)$.
\begin{lemma}\label{lem:edgefnThroughTaus}
  For an IFDS problem $P$, a node $n\in N^*$, and fact $d\in D$, let $p\in\mathsf{RP}(n,\,d)$ be a realizable path and $r\in R$ a receiver. Then there exists a non-negative number $\gamma$ of calls on the receiver $r$ with signatures $s_\gamma$ to the functions~$f_\gamma$, for which
  \[
    \ccedgefn{\{r\}}(p)(\topcc)(r)=
      \bigcap_{\gamma\ge0}\tau(s_\gamma,\,f_\gamma)\,.
  \]
\end{lemma}
\begin{proof}
  Let $p$ have the following form\footnote{It can be shown from the definition of a pointwise representation in~Sagiv et al.~\cite{sagiv1996precise} that in a realizable path, there is never an edge from a fact of the set $D$ to a $\mathbf0$ fact. Therefore, we can represent $p$ as a sequence of nodes that has a prefix of $\mathbf0$-fact nodes, after which all nodes are non-$\mathbf0$ facts.}:
  \[
    p=[(\startmain,\,\mathbf0),\,(n_1,\,\mathbf0),\,\dots,\,(n_k,\,\mathbf0),
       (n_{k+1},\,d_{k+1}),\,\dots,\,(n_{k+l},\,d_{k+l})]\,,
  \]
  where $l\ge1$ and the facts for all nodes up to $n_k$ are equal to $\mathbf0$ and $d_{k+i}\in D$ for $0<i\le l$.

@@

  From~\eqref{eq:edgefndef} we can infer that
  \[
    \ccedgefn{\{r\}}(p)=
    \ccedgefn{\{r\}}(e_{k+l})
    \circ\ldots
    \circ\ccedgefn{\{r\}}(e_{k+2})
    \circ(\lambda m\,.\,\beta)
    \circ\id
    \circ\ldots
    \circ\id\,,
  \]
  where
  \[
    \beta=
    \begin{cases}
      \botcc[r\to\tau(s,\,f)]&\text{if $(n_k,\,n_{k+1})$ is a call-start or end-return edge, and}\\&\text{the call site $r.c()$ with signature $s$ to the function}\\
      &\text{$f$ corresponds to the call-start or end-return edge,}\\
      \botcc&\text{otherwise\footnotemark.}
    \end{cases}
  \]
  \footnotetext{Since $d_k=\mathbf0$ and $d_{k+1}\ne\mathbf0$, the micro function for the edge $e_{k+1} $ is equal to $\lambda m\,.\,\varepsilon_{\{r\}}(e_{k+1})(\botcc)$. From the definition of $\varepsilon_S$~\eqref{eq:varepsilon} we can see that the only case where $\varepsilon_{\{r\}}(e_{k+1})(m)$ would not be equal to $\botcc$ is when $e_{k+1}$ is call-start or end-return edge.}

@@

\textit{Induction hypothesis:}
Assume that for a path $p=[(\startmain,\,\mathbf0),\,\dots,\,(n_{k+l},\,d_{k+l})]$, the Lemma holds for $\gamma=N$, where $N\ge0$.

\textit{Induction step:}
Let $p'=[(\startmain,\,\mathbf0),\,\dots,\,(n_{k+l},\,d_{k+l}),\,(n_{k+l+1},\,d_{k+l+1})]$.

@@

\otodo{restate the lemma before the proof}
